Flexible Scientific Data Management for Plant Phenomics Research

### 2013-03-11 s4biodiv2013/PODD-S4BIODIV-Submission.tex
compress the BagIt descriptions

\section{CSIRO High Performance Compute Infrastructure}
CSIRO ASC shared facilities \cite{ASC} are used to process the raw
PlantScan\textsuperscript{\texttrademark} data to
derive data products (meshes). Raw data and meshes are ``bagged'' and stored in
the ASC archival system. ASC High Performance Compute (HPC) hosts (systems with
high processor count and large memory) are taken advantage of to create and
verify bags more rapidly than would be possible on conventional computer
systems.

BagIt is defined by an Internet Engineering Task Force (IETF) document as an
``hierarchical file packaging format for storage and transfer of arbitrary
digital content''\cite{Kunze2011}. A payload manifest details content and MD5 or SHA hashes
for content integrity verification. Data file related metadata can be stored in
pre-defined files as key-value pairs. For
PlantScan\textsuperscript{\texttrademark}, file-level metadata
includes plant barcodes, batch numbers, and plant type.

The BagIt specification does not mandate a particular archiving strategy, the
focus being upon the directory structure, special files, and integrity checking.
Bag creation and payload manifest integrity checking, tools can take advantage
of the multi-core capabilities of modern computing hardware. To suit current
needs, BagIt-conforming tools \cite{Summers} \cite{LoCBagger} were assessed and where necessary,
improvements were implemented and tested. For example, the implementation of \cite{LoCBagger}
assumed that as many threads as possible should be created for multi-threaded
operations such as bag creation and payload manifest verification. On a HPC host
with hundreds of processors, this can lead to runaway thread creation, so this
needed to be addressed. Neither \cite{Summers} nor \cite{LoCBagger} permitted payload files in a bag to
be listed. This has since been added to \cite{LoCBagger}. 
%Some functionality (not discussed
%here) present in [8] but not in \cite{Summers} was added to the latter.

@@

\subsection{Bag preparation for a DAP collection}
CSIRO’s HRPPC makes use of DAP to store collections of
PlantScan\textsuperscript{\texttrademark} raw images
and processed mesh data as bags \cite{Kunze2011}. Raw data from
PlantScan\textsuperscript{\texttrademark} local storage
(HRPPC-Store) and data processed on HPC hosts are transferred to ASC bulk
storage where image and mesh files are organised in folders by batch, then
barcode number, then subfolders for each image file type (e.g. RGB images, IR
images, LiDAR) and meshes. Bag creation is carried out via an allocated ASC HPC
job.

>>>>

@@

BagIt is defined by an Internet Engineering Task Force (IETF) document as an
``hierarchical file packaging format for storage and transfer of arbitrary
digital content''\cite{Kunze2011}. A payload manifest details content and MD5 or SHA hashes
for content integrity verification. Data file related metadata can be stored in
pre-defined files as key-value pairs.

For PlantScan\textsuperscript{\texttrademark}, file-level metadata
includes plant barcodes, batch numbers, and plant type, although the BagIt
specification does not mandate a particular archiving strategy, with the
focus being upon the directory structure, special files, and integrity checking.
% Bag creation and payload manifest integrity checking, tools can take advantage
% of the multi-core capabilities of modern computing hardware. 
To suit current
needs, BagIt-conforming tools \cite{Summers} \cite{LoCBagger} were assessed and where necessary,
improvements were implemented and tested to ensure that the tools were scalable with the size of the collections being created. 
% For example, the implementation of \cite{LoCBagger}
% assumed that as many threads as possible should be created for multi-threaded
% operations such as bag creation and payload manifest verification. On a HPC host
% with hundreds of processors, this can lead to runaway thread creation, so this
% needed to be addressed. Neither \cite{Summers} nor \cite{LoCBagger} permitted payload files in a bag to
% be listed. This has since been added to \cite{LoCBagger}. 
%Some functionality (not discussed
%here) present in [8] but not in \cite{Summers} was added to the latter.

\subsection{Bag preparation for a DAP collection}

CSIRO ASC shared facilities \cite{ASC} are used to process the raw
PlantScan\textsuperscript{\texttrademark} data to
derive data products (meshes). Raw data and meshes are collected using the BagIt format \cite{Kunze2011} and stored in
the ASC archival system. ASC High Performance Compute (HPC) hosts (systems with
high processor count and large memory) are taken advantage of to create and
verify bags more rapidly than would be possible on conventional computer
systems. The DAP to store collections of
PlantScan\textsuperscript{\texttrademark} raw images
and processed mesh data as bags . Raw data from
PlantScan\textsuperscript{\texttrademark} local storage
(HRPPC-Store) and data processed on HPC hosts are transferred to ASC bulk
storage where image and mesh files are organised in folders by batch, then
barcode number, then subfolders for each image file type (e.g. RGB images, IR
images, LiDAR) and meshes. Bag creation is carried out via an allocated ASC HPC
job.
